Abstract Binding Trees

### 2015-10-22 paper.tex
Integrate @freebroccolo's clarifications, thanks! close #9

\newcommand\Grothendieck[1]{\oint #1}
\newcommand\Comma[2]{#1 \downarrow #2}

@@

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift
to renamings of operators' parameters; via the Grothendieck construction, we
can also consider the set $\Grothendieck\Operators$ of operators
$(\Upsilon,\varrho,\vartheta)$ for
$\Member{\vartheta}{\Operators(\Upsilon,\varrho)}$.

\[
  \infer{
    \IsOperator{\Upsilon}{\vartheta}{\varrho}
  }{
    \Member{\vartheta}{\Operators(\Upsilon,\varrho)}
  }
\]

@@

Operators are defined by specifying the fibres of $\Grothendieck\Operators$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{\cdot}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{\cdot}{\cdot}{\SortExp},
      \MkValence{\cdot}{\cdot}{\SortExp}
    }{\SortExp}
  }
\end{gather*}

>>>>

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\langle #1, #2 \rangle}

\newcommand\Comma[2]{#1 \downarrow #2}

@@

Via the Grothendieck construction\footnote{Category of elements.}
$\Grothendieck{}{}$ on the operator presheaf $\Operators$ we also have a
category with objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\Member{\vartheta}{f^{*}\Operators} = \vartheta'$.

\[
  \infer{
    \IsOperator{\Upsilon}{\vartheta}{\varrho}
  }{
    \Member{\vartheta}{\Operators\langle\Upsilon,\varrho\rangle}
  }
\]

@@

Operators are defined by specifying the fibres of $\Grothendieck{}{\Operators}$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{\cdot}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{\cdot}{\cdot}{\SortExp},
      \MkValence{\cdot}{\cdot}{\SortExp}
    }{\SortExp}
  }
\end{gather*}
